
\documentstyle[11pt]{article}

\pagestyle{empty}

\begin{document}

\begin{center}
\LARGE {\bf Publications for Alexandros Potamianos}
\end{center}

\vspace*{3mm}

\begin{itemize}

\item
G.~Potamianos and A.~Potamianos, ``Speaker adaptation for audio-visual speech
  recognition,'' in {\em Proc. European Conf. on Speech Communications and
  Technology}, (Budapest, Hungary), Sept. 1999.

\item
S.~Narayanan, A.~Potamianos, and H.~Wang, ``Multimodal systems for children:
  Building a prototype,'' in {\em Proc. European Conf. on Speech Communications
  and Technology}, (Budapest, Hungary), Sept. 1999.

\item
A.~Potamianos, G.~Riccardi, and S.~Narayanan, ``Categorical understanding using
  statistical n-gram models,'' in {\em Proc. European Conf. on Speech
  Communications and Technology}, (Budapest, Hungary), Sept. 1999.

\item
S.~Lee, A.~Potamianos, and S.~Narayanan, ``Acoustics of children's speech:
  Developmental changes of temporal and spectral parameters,'' {\em Journal of
  the Acoustical Society of America}, pp.~1455--1468, Mar. 1999.

\item
P.Maragos and A.~Potamianos, ``Fractal dimensions of speech sounds: Computation
  and application to automatic speech recognition,'' {\em Journal of the
  Acoustical Society of America}, pp.~1925--1932, Mar. 1999.

\item
G.~Riccardi, A.~Potamianos, and S.~Narayanan, ``Language model adaptation for
  spoken dialog systems,'' in {\em Internat. Conf. Speech Language Processing},
  (Australia), Oct. 1998.

\item
S.~Okawa, E.~Brocchieri, and A.~Potamianos, ``Multi--band speech recognition in
  noisy environments,'' in {\em Proc. Internat. Conf. on Acoust., Speech, and
  Signal Process.}, (Seattle, Washington), May 1998.

\item
A.~Potamianos and S.~Narayanan, ``Spoken dialog systems for children,'' in {\em
  Proc. Internat. Conf. on Acoust., Speech, and Signal Process.},
  (Seattle,Washington), pp.~197--201, May 1998.

\item
A.~Potamianos and P.~Maragos, ``Speech analysis and synthesis using an
  {AM}--{FM} modulation model,'' in {\em Proc. European Conf. on Speech
  Communications and Technology}, (Rhodes, Greece), pp.~1355--1358, Sept. 1997.

\item
P.~Maragos and A.~Potamianos, ``On using fractal features of speech sounds in
  automatic speech recognition,'' in {\em Proc. European Conf. on Speech
  Communications and Technology}, (Rhodes, Greece), pp.~2531--2534, Sept. 1997.

\item
I.~Zeljkovi\'c, S.~Narayanan, and A.~Potamianos, ``Unsupervised hmm adaptation
  based on speech-silence discrimination,'' in {\em Proc. European Conf. on
  Speech Communications and Technology}, (Rhodes, Greece), pp.~2055--2058,
  Sept. 1997.

\item
A.~Potamianos, S.~Narayanan, and S.~Lee, ``Automatic speech recognition for
  children,'' in {\em Proc. European Conf. on Speech Communications and
  Technology}, (Rhodes, Greece), pp.~2371--2374, Sept. 1997.

\item
S.~Lee, A.~Potamianos, and S.~Narayanan, ``Analysis of children's speech:
  Duration, pitch and formants,'' in {\em Proc. European Conf. on Speech
  Communications and Technology}, (Rhodes, Greece), pp.~473--476, Sept. 1997.

\item
A.~Potamianos and R.~C. Rose, ``On combining frequency warping and spectral
  shaping in {HMM}-based speech recognition,'' in {\em Proc. Internat. Conf. on
  Acoust., Speech, and Signal Process.}, (Munich, Germany), Apr. 1997.

\item
A.~Potamianos and P.~Maragos, ``Speech formant frequency and bandwidth tracking
  using multiband energy demodulation,'' {\em Journal of the Acoustical Society
  of America}, vol.~99, pp.~3795--3806, June 1996.

\item
A.~Potamianos and R.~C. Rose, ``A feature-space transformation for telephone
  based speech recognition,'' in {\em Proc. European Conf. on Speech
  Communications and Technology}, (Madrid, Spain), Sept. 1995.

\item
P.~Maragos and A.~Potamianos, ``Higher--order differential energy operators,''
  {\em IEEE Signal Processing Letters}, vol.~2, Aug. 1995.

\item
P.~Maragos, A.~Potamianos, and B.~Santhanam, ``Instantaneous energy operators:
  Applications to speech processing and communications,'' in {\em IEEE Workshop
  on Nonlinear Signal and Image Processing}, (Thessaloniki, Greece), June 1995.

\item
A.~Potamianos and P.~Maragos, ``Speech formant frequency and bandwidth tracking
  using multiband energy demodulation,'' in {\em Proc. Internat. Conf. on
  Acoust., Speech, and Signal Process.}, (Detroit, MI), May 1995.

\item
A.~Potamianos and P.~Maragos, ``Applications of speech processing using an
  {AM}--{FM} modulation model and energy operators,'' in {\em Proc. European
  Signal Process. Conf.}, (Edinburgh, Scotland), pp.~III: 1669--1672, Sept.
  1994.

\item
A.~Potamianos and P.~Maragos, ``A comparison of the energy operator and the
  {H}ilbert transform approach to signal and speech demodulation,'' {\em Signal
  Processing}, vol.~37, pp.~95--120, May 1994.

\item
H.~M. Hanson, P.~Maragos, and A.~Potamianos, ``A system for finding speech
  formants and modulations via energy separation,'' {\em IEEE Transactions on
  Speech and Audio Processing}, vol.~2, pp.~436--443, July 1994.

\item
H.~M. Hanson, P.~Maragos, and A.~Potamianos, ``Finding speech formants and
  modulations via energy separation: With application to a vocoder,'' in {\em
  Proc. Internat. Conf. on Acoust., Speech, and Signal Process.}, (Minneapolis,
  MN), Apr. 1993.

\item
J.~Diamesis and A.~Potamianos, ``Tridiagonal state-space realization of a class
  of 2-{D} transfer functions,'' in {\em Proc. of the 25th Conf. on Information
  Sciences and Systems}, (Baltimore, MD), pp.~249--253, 1991.

\end{itemize}

\end{document}

