

\documentstyle{article}
\setlength{\textwidth}{6.35 in}
\setlength{\evensidemargin}{0.000 in}
\setlength{\oddsidemargin}{0.000 in}
\setlength{\textheight}{8.80 in}
\setlength{\topmargin}{ -0.25 in}

\pagestyle{empty}


\begin{document}

\section*{Journal Publications}

\begin{enumerate}

\item
M.~Perakakis and A.~Potamianos, ``A study in efficiency and modality usage in
  multimodal form filling systems,'' {\em IEEE Transactions on Audio, Speech
  and Language Processing},  submitted, 2007.

\item
E.~Ammicht, E.~Fosler-Lussier, and A.~Potamianos, ``Information seeking spoken
  dialogue systems -- {P}art {I}: Semantics and pragmatics,'' {\em IEEE
  Transactions on Multimedia}, Apr. 2007.

\item
A.~Potamianos, E.~Fosler-Lussier, E.~Ammicht, and M.~Perakakis, ``Information
  seeking spoken dialogue systems -- {P}art {II}: Multimodal dialogue,'' {\em
  IEEE Transactions on Multimedia}, Apr. 2007.

\item
D.~Dimitriadis, P.~Maragos, and A.~Potamianos, ``Robust AM-FM features for
  speech recognition,'' {\em IEEE Signal Processing Letters}, vol.~12,
  pp.~621--624, Sept. 2005.

\item
A.~Potamianos, S.~Narayanan, and G.~Riccardi, ``Adaptive categorical
  understanding for spoken dialogue systems,'' {\em IEEE Transactions on Speech
  and Audio Processing}, vol.~13, pp.~321--329, May 2005.

\item
A.~Pargellis, E.~Fosler-Lussier, C.-H. Lee, A.~Potamianos, and A.~Tsai,
  ``Auto-induced semantic classes,'' {\em Speech Communication}, vol.~43,
  pp.~183--203, Aug. 2004.

\item
A.~Potamianos and S.~Narayanan, ``Robust recognition of children's speech,''
  {\em IEEE Transactions on Speech and Audio Processing}, vol.~11,
  pp.~603--616, Nov. 2003.

\item
V.~Weerackody, W.~Reichl, and A.~Potamianos, ``An error-protected speech
  recognition system for wireless communications,'' {\em IEEE Transactions on
  Wireless Communications}, vol.~1, pp.~282--291, Apr. 2002.

\item
S.~Narayanan and A.~Potamianos, ``Creating conversational interfaces for
  children,'' {\em IEEE Transactions on Speech and Audio Processing}, vol.~10,
  pp.~65--78, Feb. 2002.

\item
D.~Dimitriadis, V.~Pitsikalis, P.~Maragos, and A.~Potamianos, ``Modulation and
  chaotic features for speech recognition,'' {\em invited paper to the Journal
  of Control and Intelligent Systems, Special Issue on Nonlinear Speech
  Processing}, vol.~30, pp.~19--26, Jan. 2002.

\item
A.~Potamianos and P.~Maragos, ``Time-frequency distributions for automatic
  speech recognition,'' {\em IEEE Transactions on Speech and Audio Processing},
  vol.~9, pp.~196--200, Mar. 2001.

\item
A.~Potamianos and P.~Maragos, ``Speech analysis and synthesis using an
  {AM}--{FM} modulation model,'' {\em Speech Communication}, vol.~28,
  pp.~195--209, July 1999.

\item
S.~Lee, A.~Potamianos, and S.~Narayanan, ``Acoustics of children's speech:
  Developmental changes of temporal and spectral parameters,'' {\em Journal of
  the Acoustical Society of America}, pp.~1455--1468, Mar. 1999.

\item
P.Maragos and A.~Potamianos, ``Fractal dimensions of speech sounds: Computation
  and application to automatic speech recognition,'' {\em Journal of the
  Acoustical Society of America}, pp.~1925--1932, Mar. 1999.

\item
A.~Potamianos and P.~Maragos, ``Speech formant frequency and bandwidth tracking
  using multiband energy demodulation,'' {\em Journal of the Acoustical Society
  of America}, vol.~99, pp.~3795--3806, June 1996.

\item
P.~Maragos and A.~Potamianos, ``Higher--order differential energy operators,''
  {\em IEEE Signal Processing Letters}, vol.~2, Aug. 1995.

\item
H.~M. Hanson, P.~Maragos, and A.~Potamianos, ``A system for finding speech
  formants and modulations via energy separation,'' {\em IEEE Transactions on
  Speech and Audio Processing}, vol.~2, pp.~436--443, July 1994.

\item
A.~Potamianos and P.~Maragos, ``A comparison of the energy operator and the
  {H}ilbert transform approach to signal and speech demodulation,'' {\em Signal
  Processing}, vol.~37, pp.~95--120, May 1994.

\end{enumerate}

\newpage


\section*{Conference Publications}

\begin{enumerate}

\item
E.~Iosif and A.~Potamianos, ``Unsupervised semantic similarity computation
  using web search engines,'' in {\em Proc. Intern. Conf. on Web Intelligence},
  (Silicon Valley, USA), Nov. 2007.

\item
E.~Sanchez-Soto, K.~Daoudi, and A.~Potamianos, ``Unsupervised stream weight
  computation in a segmentation task: Application to audio-visual speech
  recognition,'' in {\em Proc. Intern. Conf. on Signal Proc. and
  Communications}, (Dubai, UAE), Nov. 2007.

\item
M.~Perakakis and A.~Potamianos, ``The effect of input mode on inactivity and
  interaction times of multimodal systems,'' in {\em Internat. Conf. on
  Multimodal Interfaces}, (Nagoya, Japan), Nov. 2007.

\item
A.~Potamianos and S.~Narayanan, ``A review of the acoustic and linguistic
  properties of children's speech,'' in {\em Proc. Intern. Workshop on
  Multimedia Signal Processing}, (Chania, Greece), Oct. 2007.

\item
{S.~Siltanen et al}, ``Multimodal user interface for augmented assembly,'' in
  {\em Proc. Intern. Workshop on Multimedia Signal Processing}, (Chania,
  Greece), Oct. 2007.

\item
E.~Iosif and A.~Potamianos, ``A soft-clustering algorithm for automatic
  induction of semantic classes,'' in {\em Proc. Interspeech}, (Antwerp,
  Belgium), Aug. 2007.

\item
D.~Dimitriadis, J.~Segura, L.~Garcia, A.~Potamianos, P.~Maragos, and
  V.~Pitsikalis, ``Advanced front-end for robust speech recognition in
  extremely adverse environments,'' in {\em Proc. Interspeech}, (Antwerp,
  Belgium), Aug. 2007.

\item
A.~Katsamanis, P.~Tsiakoulis, P.~Maragos, and A.~Potamianos, ``Investigations
  in articulatory synthesis,'' in {\em Proc. Intenat. Conf. on Phonetics},
  (Saarbrucken, Germany), Aug. 2007.

\item
E.~Sanchez-Soto, A.~Potamianos, and K.~Daoudi, ``Unsupervised stream weight
  computation using anti-models,'' in {\em Proc. Internat. Conf. on Acoust.,
  Speech, and Signal Process.}, (Hawaii, USA), Apr. 2007.

\item
E.~Iosif, A.~Tegos, A.~Pangos, E.~Fosler-Lussier, and A.~Potamianos,
  ``Unsupervised combination of metrics for semantic class induction,'' in {\em
  IEEE/ACM Workshop on Spoken Language Technology}, (Aruba), Dec. 2006.

\item
M.~Perakakis, M.~Toutoudakis, and A.~Potamianos, ``Blending speech and visual
  input in multimodal dialogue systems,'' in {\em IEEE/ACM Workshop on Spoken
  Language Technology}, (Aruba), Dec. 2006.

\item
M.~Toutoudakis, M.~Perakakis, and A.~Potamianos, ``Mode selection in multimodal
  dialogue systems,'' {\em invited paper to ICYC}, (Agia Napa, Cyprus), July
  2006.

\item
A.~{Potamianos et al}, ``Towards speaker and enviromental robustness in {ASR}:
  the {HIWIRE} project,'' in {\em ITRW Workshop on Speech Recognition and
  Intrinsic Variation}, (Toulouse, France), May 2006.

\item
A.~Potamianos, E.~Sanchez-Soto, and K.~Daoudi, ``Stream weight computation for
  multi-stream classifiers,'' in {\em Proc. Internat. Conf. on Acoust., Speech,
  and Signal Process.}, (Toulouse, France), May 2006.

\item
K.~Mokios, N.~Sidiropoulos, and A.~Potamianos, ``Blind speech separation
  algorithm using {PARAFAC} and integer least squares,'' in {\em Proc.
  Internat. Conf. on Acoust., Speech, and Signal Process.}, (Toulouse, France),
  May 2006.

\item
P.~Karageorgakis, A.~Potamianos, and I.~Klasinas, ``Towards incorporating
  language morphology into statistical machine translation systems,'' in {\em
  Proc. Automatic Speech Recogn. and Underst. Workshop}, (Cancun, Mexico), Dec.
  2005.

\item
A.~Pangos, E.~Iosif, A.~Potamianos, and E.~Fosler-Lussier, ``Combining
  statistical similarity measures for automatic induction of semantic
  classes,'' in {\em Proc. Automatic Speech Recogn. and Underst. Workshop},
  (Cancun, Mexico), Dec. 2005.

\item
M.~Perakakis, M.~Toutoudakis, and A.~Potamianos, ``Modality selection for
  multimodal dialogue systems,'' in {\em Internat. Conf. on Multimodal
  Interfaces}, (Trento, Italy), Oct. 2005.

\item
D.~Dimitriadis, P.~Maragos, and A.~Potamianos, ``Auditory teager energy
  cepstrum coefficients for robust speech recognition,'' in {\em Proc. European
  Conf. on Speech Communication and Technology}, (Lisbon, Portugal), Sept.
  2005.

\item
S.~Yildirim, C.~Lee, S.~Lee, A.~Potamianos, and S.~Narayanan, ``Detecting
  politeness and frustration state of a child in a conversational computer
  game,'' in {\em Proc. European Conf. on Speech Communication and Technology},
  (Lisbon, Portugal), Sept. 2005.

\item
A.~Potamianos, E.~Ammicht, and E.~Fosler-Lussier, ``Modality tracking in the
  multimodal {B}ell {L}abs {C}ommunicator,'' in {\em Proc. Automatic Speech
  Recogn. and Underst. Workshop}, (St. Thomas, U.S. Virgin Islands), Dec. 2003.

\item
A.~Potamianos, ``Novel features for robust speech recognition,'' in {\em
  invited presentation to the Conf. of the Acoustical Society of America},
  (Cancun, Mexico), Dec. 2002.

\item
M.~{Walker et al}, ``{DARPA} {C}ommunicator: Cross-system results for the 2001
  evaluation,'' in {\em Internat. Conf. Speech Language Processing},
  (Colorado), Sept. 2002.

\item
M.~{Walker et al}, ``{DARPA} {C}ommunicator evaluation: Progress from 2000 to
  20001,'' in {\em Internat. Conf. Speech Language Processing}, (Colorado),
  Sept. 2002.

\item
R.~Argiles-Solsona, E.~Fosler-Lussier, J.~Kuo, A.~Potamianos, and I.~Zitouni,
  ``Adaptive language models for spoken dialogue systems,'' in {\em Proc.
  Internat. Conf. on Acoust., Speech, and Signal Process.}, (Orlando, Florida),
  May 2002.

\item
D.~Dimitriadis, P.~Maragos, and A.~Potamianos, ``Modulation features for speech
  recognition,'' in {\em Proc. Internat. Conf. on Acoust., Speech, and Signal
  Process.}, (Orlando, Florida), May 2002.

\item
S.~Lee, E.~Ammicht, E.~Fosler-Lussier, J.~Kuo, and A.~Potamianos, ``Spoken
  dialogue evaluation for the {B}ell {L}abs {C}ommunicator system,'' in {\em
  Proc. Human Language Technology Conf.}, (San Diego, California), Mar. 2002.

\item
M.~Tsangaris and A.~Potamianos, ``{AGORA}: A {GUI} approach to multimodal user
  interfaces,'' in {\em Proc. Human Language Technology Conf.}, (San Diego,
  California), Mar. 2002.

\item
E.~Ammicht, A.~Potamianos, and E.~Fosler-Lussier, ``Ambiguity representation
  and resolution in spoken dialogue systems,'' in {\em Proc. European Conf. on
  Speech Communication and Technology}, (Aalborg, Denmark), Oct. 2001.

\item
M.~Galley, E.~Fosler-Lussier, and A.~Potamianos, ``Hybrid natural language
  generation for spoken dialogue systems,'' in {\em Proc. European Conf. on
  Speech Communication and Technology}, (Aalborg, Denmark), Oct. 2001.

\item
A.~Pargellis, E.~Fosler-Lussier, A.~Potamianos, and C.-H. Lee, ``Metrics for
  measuring domain-independence of semantic classes,'' in {\em Proc. European
  Conf. on Speech Communication and Technology}, (Aalborg, Denmark), Oct. 2001.

\item
M.~{Walker et al}, ``{DARPA} {C}ommunicator dialog travel planning systems: the
  {J}une 2000 evaluation,'' in {\em Proc. European Conf. on Speech
  Communication and Technology}, (Aalborg, Denmark), Oct. 2001.

\item
A.~Potamianos and V.~Weerackody, ``Soft-feature decoding for speech recognition
  over wireless channels,'' in {\em Proc. Internat. Conf. on Acoust., Speech,
  and Signal Process.}, (Salt Lake City, Utah), May 2001.

\item
A.~Pargellis and A.~Potamianos, ``Cross-domain classification using generalized
  domain acts,'' in {\em Internat. Conf. Speech Language Processing}, (Beijing,
  China), Oct. 2000.

\item
A.~Potamianos, E.~Ammicht, and H.-K. Kuo, ``Dialogue management in the {B}ell
  {L}abs communicator system,'' in {\em Internat. Conf. Speech Language
  Processing}, (Beijing, China), Oct. 2000.

\item
A.~Potamianos and H.-K. Kuo, ``Speech understanding using finite state
  transducers,'' in {\em Internat. Conf. Speech Language Processing}, (Beijing,
  China), Oct. 2000.

\item
W.~Reichl, V.~Weerackody, and A.~Potamianos, ``A codec for speech recognition
  in a wireless system,'' in {\em Proc. EUROCOMM}, (Munich, Germany), May 2000.

\item
A.~Potamianos and P.~Maragos, ``Time-frequency distributions for automatic
  speech recognition,'' in {\em Proc. Workshop on Automatic Speech Recognition
  and Understanding}, (Keystone, Colorado), Dec. 1999.

\item
S.~Narayanan, A.~Potamianos, and H.~Wang, ``Multimodal systems for children:
  Building a prototype,'' in {\em Proc. European Conf. on Speech Communication
  and Technology}, (Budapest, Hungary), Sept. 1999.

\item
G.~Potamianos and A.~Potamianos, ``Speaker adaptation for audio-visual speech
  recognition,'' in {\em Proc. European Conf. on Speech Communication and
  Technology}, (Budapest, Hungary), Sept. 1999.

\item
A.~Potamianos, G.~Riccardi, and S.~Narayanan, ``Categorical understanding using
  statistical n-gram models,'' in {\em Proc. European Conf. on Speech
  Communication and Technology}, (Budapest, Hungary), Sept. 1999.

\item
A.~{Potamianos et al}, ``Design principles and tools for multimodal dialog
  systems,'' in {\em Proc. ESCA Workshop Interact. Dialog. Multi-Modal Syst.},
  (Kloster Irsee, Germany), June 1999.

\item
G.~Riccardi, A.~Potamianos, and S.~Narayanan, ``Language model adaptation for
  spoken dialog systems,'' in {\em Internat. Conf. Speech Language Processing},
  (Australia), Oct. 1998.

\item
S.~Okawa, E.~Brocchieri, and A.~Potamianos, ``Multi--band speech recognition in
  noisy environments,'' in {\em Proc. Internat. Conf. on Acoust., Speech, and
  Signal Process.}, (Seattle, Washington), May 1998.

\item
A.~Potamianos and S.~Narayanan, ``Spoken dialog systems for children,'' in {\em
  Proc. Internat. Conf. on Acoust., Speech, and Signal Process.},
  (Seattle,Washington), pp.~197--201, May 1998.

\item
S.~Lee, A.~Potamianos, and S.~Narayanan, ``Analysis of children's speech:
  Duration, pitch and formants,'' in {\em Proc. European Conf. on Speech
  Communication and Technology}, (Rhodes, Greece), pp.~473--476, Sept. 1997.

\item
P.~Maragos and A.~Potamianos, ``On using fractal features of speech sounds in
  automatic speech recognition,'' in {\em Proc. European Conf. on Speech
  Communication and Technology}, (Rhodes, Greece), pp.~2531--2534, Sept. 1997.

\item
A.~Potamianos and P.~Maragos, ``Speech analysis and synthesis using an
  {AM}--{FM} modulation model,'' in {\em Proc. European Conf. on Speech
  Communication and Technology}, (Rhodes, Greece), pp.~1355--1358, Sept. 1997.

\item
A.~Potamianos, S.~Narayanan, and S.~Lee, ``Automatic speech recognition for
  children,'' in {\em Proc. European Conf. on Speech Communication and
  Technology}, (Rhodes, Greece), pp.~2371--2374, Sept. 1997.

\item
I.~Zeljkovi\'c, S.~Narayanan, and A.~Potamianos, ``Unsupervised {HMM}
  adaptation based on speech-silence discrimination,'' in {\em Proc. European
  Conf. on Speech Communication and Technology}, (Rhodes, Greece),
  pp.~2055--2058, Sept. 1997.

\item
A.~Potamianos and R.~C. Rose, ``On combining frequency warping and spectral
  shaping in {HMM}-based speech recognition,'' in {\em Proc. Internat. Conf. on
  Acoust., Speech, and Signal Process.}, (Munich, Germany), Apr. 1997.

\item
R.~C. Rose and A.~Potamianos, ``Improving robustness in {HMM} based speech
  recognition through simultaneous frequency warping and spectral shaping,'' in
  {\em {ESCA}--{NATO} Workshop on Robust Speech Recognition}, (Pont-a-Mousson,
  France), Apr. 1997.

\item
A.~Potamianos and R.~C. Rose, ``A feature-space transformation for telephone
  based speech recognition,'' in {\em Proc. European Conf. on Speech
  Communication and Technology}, (Madrid, Spain), Sept. 1995.

\item
P.~Maragos, A.~Potamianos, and B.~Santhanam, ``Instantaneous energy operators:
  Applications to speech processing and communications,'' in {\em IEEE Workshop
  on Nonlinear Signal and Image Processing}, (Thessaloniki, Greece), June 1995.

\item
A.~Potamianos and P.~Maragos, ``Speech formant frequency and bandwidth tracking
  using multiband energy demodulation,'' in {\em Proc. Internat. Conf. on
  Acoust., Speech, and Signal Process.}, (Detroit, MI), May 1995.

\item
A.~Potamianos and P.~Maragos, ``Applications of speech processing using an
  {AM}--{FM} modulation model and energy operators,'' in {\em Proc. European
  Signal Process. Conf.}, (Edinburgh, Scotland), pp.~III: 1669--1672, Sept.
  1994.

\item
P.~Maragos, T.~F. Quatieri, J.~F. Kaiser, and A.~Potamianos, ``Demodulation of
  {AM}--{FM} resonances in speech using energy separation,'' in {\em
  presentation to the Conf. of the Acoustical Society of America}, (Boston,
  MA), June 1994.

\item
H.~M. Hanson, P.~Maragos, and A.~Potamianos, ``Finding speech formants and
  modulations via energy separation: With application to a vocoder,'' in {\em
  Proc. Internat. Conf. on Acoust., Speech, and Signal Process.}, (Minneapolis,
  MN), Apr. 1993.

\item
J.~Diamesis and A.~Potamianos, ``Tridiagonal state-space realization of a class
  of 2-{D} transfer functions,'' in {\em Proc. of the 25th Conf. on Information
  Sciences and Systems}, (Baltimore, MD), pp.~249--253, Mar. 1991.

\end{enumerate}

\newpage

\section*{Awarded Patents}

\begin{enumerate}

\item
V.~Weerackody, W.~Reichl and A.~Potamianos, 
``Soft feature decoding in a distributed automatic speech recognition system for use over wireless channels,'' in {\em US patent no. 6,760,699}, July 2004.

\item
S.~Narayanan, A.~Potamianos, and I.~Zeljkovi\'c, ``Unsupervised {HMM}
  adaptation based on speech-silence discrimination,'' in {\em US patent no.
  6,076,057}, June 2000.

\item
A.~Potamianos and R.~C. Rose, ``On combining frequency warping and spectral
  shaping in {HMM}-based speech recognition,'' in {\em US patent no.
  5,930,753}, July 1999.

\item
A.~Potamianos and R.~C. Rose, ``Time-varying feature space preprocessing
  procedure for telephone-based speech recognition,'' in {\em US patent no.
  5,765,124}, June 1998.

\end{enumerate}

\newpage

\section*{Thesis}

A. Potamianos, ``Speech Processing Applications Using an AM-FM Modulation Model,'' 
{\em Division of Applied Sciences, Harvard University}, (Cambridge, MA), 1996

\end{document}
